Numerical Stability of Detonations in White Dwarf Simulations

### 2018-07-10 papers/ignition/paper.tex
Very rough first cut at the new abstract

%==========================================================================
% Abstract
%==========================================================================
\begin{abstract}
Simulations of white dwarf mergers that include thermonuclear reactions must
confront the question of how nuclear detonations form and whether observed
detonations in a numerical simulation are realistic. We address this question
by performing simulations of collisions of white dwarfs, a subset of white
dwarf mergers that occur when the stars approach each other nearly head-on.
These have the potential for explosive nucleosynthesis, leading to a thermonuclear
detonation that disrupts both stars, possibly causing a Type Ia supernova.
While this story is intuitively plasible, demonstrating this in a reacting
hydrodynamics simulation is challenging due to the rapid evolution of the
nuclear burning, posing numerical challenges related to both spatial and
temporal resolution. In this study we explore a number of the algorithmic choices
that affect the outcome of reacting hydrodynamics simulations, and address
the question of what is required to ensure that these simulations are properly
converged. We find that achieving a converged white dwarf collision simulation
in the code \castro\ is very difficult. The typical timesteps taken by hydrodynamics
codes are too large, and the achievable spatial resolution is too low, while increasing
either to the point required to actually obtain a converged simulation is
prohibitive. We have identified a criterion for adaptive mesh refinement
that covers the most important regions in the simulation and allows us to
achieve very high resolution in the burning region. However, even in our
highest resolution simulations, we do not find a converged result, and
detonations seem to occur stochastically. Our results point to a path forward
for astrophysical simulations with thermonuclear detonations, but for now
they encourage severe caution in interpreting observed detonations in previous
and current simulations.
\end{abstract}
\keywords{supernovae: general - white dwarfs}

>>>>

%==========================================================================
% Abstract
%==========================================================================
\begin{abstract}
Some simulations of Type Ia supernovae feature thermonuclear detonations that
arise naturally during the evolution. It is usually not clear whether these
detonations occur in the same time and place as they would in a simulation
that fully resolved the burning length scale (assuming the resolved simulation
even features a detonation). In this study we explore a number of the algorithmic
choices that affect the outcome of reacting hydrodynamics simulations, and address
the question of what is required to ensure that these simulations are properly
converged. We focus on the spatial and temporal resolution, as well as the coupling
between the hydrodynamics and the reactions. Adaptive mesh refinement, properly
targeted at the relevant burning regions, works well for achieving converged simulations
on a relatively coarse grid.
\end{abstract}
\keywords{supernovae: general - white dwarfs}
